### 2016-07-18 Projects/DelCo_2012/Report/DelCo_2012.tex
add files, scripts, report edits for CAFS

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
	\caption{Dimensioned Floor Plan of the Test Structure.}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
	\caption{Dimensioned Floor Plan of First Floor of Two Story Structure.}
	\label{fig:dimensioned_first_2story}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
	\caption{Dimensioned Floor Plan of Second Floor of Two Story Structure.}
	\label{fig:dimensioned_second_2story}
\end{figure}

@@

The structures were instrumented for temperature, gas velocity, and heat flux measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend}
	\caption{Instrumentation Legend.}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Gas Cooling Experiments.}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Single Story Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Instrumentation}
	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two Story Structure.}
	\label{fig:fire_supp_first_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation}
	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two Story Structure.}
	\label{fig:fire_supp_second_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
	\caption{Burn Building Fuel Load.}
	\label{fig:Burn_Building_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
	\caption{Furniture Fuel Load Dimensions in Single Story Structure.}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}

@@

The fuel load for experiments 9 through 12 consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly". Two stacks of pallets with hay were used as the first items ignited in each experiment. Each stack was composed of six pallets with a half bale of hay. The hay was layered between each pallet. Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition. The pallets and hay were weighed prior to each experiment. For the four pallet experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).
\begin{figure}[!ht]
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
	\caption{Photograph of Southeast corner of burn room with wood fuel load.}
	\label{fig:Wood_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load in Single Story Structure.}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
	\caption{Furniture Fuel Load in First Floor of Two-Story Structure.}
	\label{fig:furniture_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure.}
	\label{fig:pallet_furniture_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.5\columnwidth]{../Figures/Pictures/Water Tests Bins.png}
	\caption{Interlocking collecting bins used to capture suppression agent during spray density tests.}
	\label{fig:water_buckets}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Mid_BB}
	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Back_BB}
	\caption{Stream positions mid(left) and back (right) during spray density tests.}
	\label{fig:stream_position}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation2}
	\caption{Schematic of  the Gas Cooling Experiments.}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions2}
\end{figure}
Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3. As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the mid position compared to the positions of the thermocouple trees.
\begin{figure}[!ht]
	\includegraphics[width=.7\columnwidth]{../Figures/Bars/BB18b}
	\caption{Gas Cooling Spray Density Test 18, CAF, Straight Stream}
	\label{fig:Burn_Building_Test_18b}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
	\label{fig:fs_hall_a2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
	\label{fig:fs_door_a2}
\end{figure}

@@

There were 7 suppression tests conducted in the two story purpose-built structure. All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor south door. The fires were intended to replicate room and contents basement fires typically seen within residential structures. Suppression occurred at the basement double doors of the structure. Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.

\begin{table}[!ht]
\centering
\footnotesize
\caption{Two Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    & Ventilation  \\
\midrule
 13  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Doors, 1st Floor Door \\
 14  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Doors, 1st Floor Door \\
 15  & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 16  & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 17  & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 18  & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 19  & CAF~9a    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 20  & CAF~9b    &  Solid Stream        &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAF tests conducted in the two story structure. The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floor. This remote measurement location provides that is isolated from any direct contact from the suppression stream. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door. The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.

\begin{table}[!ht]
\centering
\caption{Two Story Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
\begin{tabular}{lcccc}
\toprule[1.5pt]
           &               & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               & 1~m Above Floor \\
\midrule
CAF~7      & 24            & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7    & 29            & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a     & 16            & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b     & 21            & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Water~8    & 18            & 440~$^{\circ}$C - 295~$^{\circ}$C   & 375~$^{\circ}$C - 250~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
Class A~1  & 19            & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a     & 21            & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b     & 16            & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to Water, but the differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.

@@

\subsection{National Fire Academy (1884)}
The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}. This formula sets the required fire flow, in gpm, equal to the floor area (in square feet) divided by 3.
\begin{equation}\label{eq:nfa_form}
required fire flowrate = Area / 3
\end{equation}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB1} &
\includegraphics[width=3.2in]{../Figures/Bars/BB2} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB3} &
\includegraphics[width=3.2in]{../Figures/Bars/BB4}
\end{tabular*}
\caption{Spray density figures for burn building tests 1) Water Straight Stream Back (upper left), 2) Water Straight Stream Back (upper right), 3) Water Straight Stream Mid (lower left), and 4) Water Straight Stream Mid (lower right).}
\label{fig:bb_1_4}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB5} &
\includegraphics[width=3.2in]{../Figures/Bars/BB6} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB7} &
\includegraphics[width=3.2in]{../Figures/Bars/BB8}
\end{tabular*}
\caption{Spray density figures for burn building tests 5) Water Straight Stream Mid (upper left), 6) Water Fog Mid (upper right), 7) Water Fog Mid (lower left), and 8) Water Fog Back (lower right).}
\label{fig:bb_5_8}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB9} &
\includegraphics[width=3.2in]{../Figures/Bars/BB10} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB11} &
\includegraphics[width=3.2in]{../Figures/Bars/BB12}
\end{tabular*}
\caption{Spray density figures for burn building tests 9) Water Fog Back (upper left), 10) Water Solid Stream Back (upper right), 11) Water Solid Stream Back (lower left), and 12) CAF Solid Stream Back (lower right).}
\label{fig:bb_9_12}
\end{figure}

@@

>>>>

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
	\caption{Dimensioned Floor Plan of the Test Structure}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
	\caption{Dimensioned Floor Plan of First Floor of Two Story Structure}
	\label{fig:dimensioned_first_2story}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
	\caption{Dimensioned Floor Plan of Second Floor of Two Story Structure}
	\label{fig:dimensioned_second_2story}
\end{figure}

@@

The structures were instrumented for temperature, gas velocity, and heat flux measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single, sheathed thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple was protected with an 3.2~mm (0.125~in) diameter inconel sheath. The sheathing protects the thermocouple from water but slows the response time because of the additional thermal mass. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend}
	\caption{Instrumentation Legend}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Gas Cooling Experiments}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
	\caption{Instrumentation Schematic for the Single Story Fire Suppression Experiments}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Instrumentation}
	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two Story Structure}
	\label{fig:fire_supp_first_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation}
	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two Story Structure}
	\label{fig:fire_supp_second_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
	\caption{Burn Building Fuel Load}
	\label{fig:Burn_Building_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
	\caption{Furniture Fuel Load Dimensions in Single Story Structure}
	\label{fig:Furniture_Fuel_Load_Dimensions}
\end{figure}

@@

The fuel load for experiments 9 through 12 consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly". Two stacks of pallets with hay were used as the first items ignited in each experiment. Each stack was composed of six pallets with a half bale of hay. The hay was layered between each pallet. Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition. The pallets and hay were weighed prior to each experiment. For the four pallet experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).
\begin{figure}[!ht]
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
	\caption{Photograph of Southeast corner of burn room with wood fuel load}
	\label{fig:Wood_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load in Single Story Structure}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
	\caption{Furniture Fuel Load in First Floor of Two-Story Structure}
	\label{fig:furniture_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure}
	\label{fig:pallet_furniture_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.5\columnwidth]{../Figures/Pictures/Water Tests Bins.png}
	\caption{Interlocking collecting bins used to capture suppression agent during spray density tests}
	\label{fig:water_buckets}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Mid_BB}
	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Back_BB}
	\caption{Stream positions mid(left) and back (right) during spray density tests}
	\label{fig:stream_position}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation2}
	\caption{Schematic of  the Gas Cooling Experiments}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions2}
\end{figure}
Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3. As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the mid position compared to the positions of the thermocouple trees.
\begin{figure}[!ht]
	\includegraphics[width=.7\columnwidth]{../Figures/Bars/BB18b}
	\caption{Gas Cooling Spray Density Test 18, CAF, Straight Stream}
	\label{fig:Burn_Building_Test_18b}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
	\caption{CAF vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
	\label{fig:fs_hall_a2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
	\caption{CAF vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
	\label{fig:fs_door_a2}
\end{figure}

@@

There were 7 suppression tests conducted in the two story purpose-built structure. All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}). Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor door on the south side of the structure. The fires were intended to replicate room and contents basement fires typically seen within residential structures. Suppression occurred at the basement double doors of the structure. Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.

\begin{table}[!ht]
\centering
\footnotesize
\caption{Two Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
\begin{tabular}{clllll}
\toprule[1.5pt]
Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    & Ventilation  \\
\midrule
 13  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Doors, 1st Floor Door \\
 14  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Doors, 1st Floor Door \\
 15  & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 16  & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 17  & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 18  & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 19  & CAF~9a    &  1 3/8'' Ball    	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 20  & CAF~9b    &  Solid Stream        &  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two story structure. The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floors. The thermocouples at this measurement location were isolated from any direct contact from the suppression stream. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door. Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux guages. Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling). Note that these thermocouples are inconel shielded thermocouples and have slower reponse times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story. The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.

\begin{table}[!ht]
\centering
\caption{Two Story Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
\begin{tabular}{lcccc}
\toprule[1.5pt]
           &               & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               & 1~m Above Floor \\
\midrule
CAF~7      & 24            & 530~$^{\circ}$C - 425~$^{\circ}$C   & 670~$^{\circ}$C - 425~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7    & 29            & 560~$^{\circ}$C - 430~$^{\circ}$C   & 670~$^{\circ}$C - 400~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a     & 16            & 475~$^{\circ}$C - 425~$^{\circ}$C   & 580~$^{\circ}$C - 460~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b     & 21            & 475~$^{\circ}$C - 400~$^{\circ}$C   & 540~$^{\circ}$C - 400~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Water~8    & 18            & 520~$^{\circ}$C - 460~$^{\circ}$C   & 530~$^{\circ}$C - 440~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
Class A~1  & 19            & 470~$^{\circ}$C - 430~$^{\circ}$C   & 590~$^{\circ}$C - 500~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a     & 21            & 530~$^{\circ}$C - 440~$^{\circ}$C   & 620~$^{\circ}$C - 450~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b     & 16            & 580~$^{\circ}$C - 510~$^{\circ}$C   & 660~$^{\circ}$C - 525~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

\begin{figure}[!ht]
	\includegraphics[width=.9\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation2}
	\caption{Schematic of Second Floor of Two Story Structure Indicating Thermocouple and Heat Flux Gauges}
	\label{fig:tcs_hf_second_2story}
\end{figure}

The time history profile of the temperature response along with the heat flux at three positions are shown in Figures~\ref{fig:water7_tca10} - \ref{fig:caf9a_hf}. Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7 while Fig.~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a. The remainder of the fire suppression test data is included in Appendix~\ref{app:fire_suppression2}.

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Water~7 Fire Suppression Test}
	\label{fig:water7_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Water~7 Fire Suppression Test}
	\label{fig:water7_hf}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9a Fire Suppression Test}
	\label{fig:caf9a_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9a Fire Suppression Test}
	\label{fig:caf9a_hf}
\end{figure}

The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room. Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression. In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparalbe configurations.

\begin{figure}[!ht]
	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TC_A10_scatter}
	\caption{CAF vs Water Temperature Difference Comparison for Two Story Fire Suppression Test at Thermocouple Array A10}
	\label{fig:fs_a10}
\end{figure}

In Fig.~\ref{fig:fs_a10}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) falls within the experimental uncertainty based around the equal cooling line (solid black line). This indicates an inability to distinguish whether CAF or water had a more significant impact in temperature reduction following suppression of the fire. The R$^2$ value of 0.975 shows a strong fit to the data between water and CAF. Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to Water, but the differences are not substantial. Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.

@@

\subsection{National Fire Academy (1918)}
The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}. This formula sets the required fire flow, in gpm, equal to the floor area (in square feet) divided by 3.
\begin{equation}\label{eq:nfa_form}
required fire flowrate = Area / 3
\end{equation}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB1} &
\includegraphics[width=3.2in]{../Figures/Bars/BB2} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB3} &
\includegraphics[width=3.2in]{../Figures/Bars/BB4}
\end{tabular*}
\caption{Spray density figures for burn building tests 1) Water Straight Stream Back (upper left), 2) Water Straight Stream Back (upper right), 3) Water Straight Stream Mid (lower left), and 4) Water Straight Stream Mid (lower right)}
\label{fig:bb_1_4}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB5} &
\includegraphics[width=3.2in]{../Figures/Bars/BB6} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB7} &
\includegraphics[width=3.2in]{../Figures/Bars/BB8}
\end{tabular*}
\caption{Spray density figures for burn building tests 5) Water Straight Stream Mid (upper left), 6) Water Fog Mid (upper right), 7) Water Fog Mid (lower left), and 8) Water Fog Back (lower right)}
\label{fig:bb_5_8}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular*}{\textwidth}{lr}
\includegraphics[width=3.2in]{../Figures/Bars/BB9} &
\includegraphics[width=3.2in]{../Figures/Bars/BB10} \\
\includegraphics[width=3.2in]{../Figures/Bars/BB11} &
\includegraphics[width=3.2in]{../Figures/Bars/BB12}
\end{tabular*}
\caption{Spray density figures for burn building tests 9) Water Fog Back (upper left), 10) Water Solid Stream Back (upper right), 11) Water Solid Stream Back (lower left), and 12) CAF Solid Stream Back (lower right)}
\label{fig:bb_9_12}
\end{figure}

@@

\chapter{Two Story Fire Suppression Data}
\label{app:fire_suppression2}
